\thesistitle

### 2019-08-24 sections/results.tex
Small thesis chnages

\subsection{Clone Token Volume}
Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored. As the amount of data points decreases, the datapoints gain less statistical significance, because of which we represent the x-axis as a logaritmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

@@

The displayed return categories are ordered by their scores. Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability. When the result of the call to the extracted method is directly returns, the maintainability score is the highest. When no value is returned, the maintainability score is the lowest. The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters.

>>>>

\subsection{Clone Token Volume}
Figure \ref{fig:maintainabilityscore} shows the obtained results when plotting the clone volume vs the maintainability increase/decrease. We define the \textit{token volume} as the combined number of tokens in all clone instances in a refactored clone class. The maintainability score, as shown in Figure \ref{fig:maintainabilityscore}, is the average delta maintainability score of all clone classes with the specified token volume that are refactored. For higher token volume numbers we have less refactorings that refactor such clones, because of which we represent the x-axis as a logaritmic scale. The trendline intersects the ``zero'' line (maintainability does not increase nor decrease) at a token volume of 63.

@@

The displayed return categories are ordered by their scores. Overall, the scores do not deviate much (-0.18 to 0.19), indicating that the return category has a minor impact on maintainability. When the result of the call to the extracted method is directly returns, the maintainability score is the highest. When no value is returned, the maintainability score is the lowest. The main reason that no return value ends up lowest, is that it is linked to a higher number of parameters required for the extracted method.
